\huge A Usability Evaluation of Tor Launcher

### 2017-03-20 pets2017-paper/pets2017-paper.tex
switch first sentence to last

\subsection{Experimental Setup}
\label{sec:environments}
We simulated three environments of varying censorship severity (Table~\ref{tab:environments}). We chose to 
simulate environments for the stability and reproducibility of the experiment, as real censored networks are volatile and complex. Re-routing participant traffic through other countries' networks also may introduce unforeseen risks to the participants out of our control and performing hundreds of connections in short intervals during experiments may draw unnecessary attention to Tor use in that country.

>>>>

\subsection{Experimental Setup}
\label{sec:environments}
We chose to simulate environments for the stability and reproducibility of the experiment, as real censored networks are volatile and complex. Re-routing participant traffic through other countries' networks also may introduce unforeseen risks to the participants out of our control and performing hundreds of connections in short intervals during experiments may draw unnecessary attention to Tor use in that country. The three environments are described in Table~\ref{tab:environments}.
